---
title: "Chao-Jen Wong's CV"
author: Chao-Jen Wong
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source(file.path("/Users/cwon2/Project/datadrivencv-cjwong", 
                 "cv_printing_functions.r"))
# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1AkSxtew_rYIyTeY5mPvkxqJEQKKdjJ0ZCfJxHHYL3pk/edit#gid=917338460",  
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================


```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
datadrivencv::build_network_logo(CV$entries_data)
```



```{r, eval=FALSE}
if(params$pdf_mode){
  cat("View this CV online with links at _/Users/cwon2/Documents/resume-2022/datadrivencv-cjwong_")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](/Users/cwon2/Documents/resume-2022/datadrivencv-cjwong)")
}
```

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```



Skills {#skills}
--------------------------------------------------------------------------------

```{r}
CV %>% print_skill_bars()
```

<!--

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown). 
Last updated on `r Sys.Date()`.
-->

<!--
The source code is available [on github.com/nstrayer/cv](/Users/cwon2/Documents/resume-2022/datadrivencv-cjwong).
-->




Main
================================================================================

Chao-Jen Wong {#title}
--------------------------------------------------------------------------------

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```


<!--Research Experience {data-icon=laptop} -->
<!----------------------------------------------------------------------------------
-->

```{r}
#CV %<>% print_section('research_positions')
```


Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------
<!--
::: aside
```{r}
CV %<>% print_text_block('industy_experience_aside')
```
:::
-->

```{r}
CV %<>% print_section('industry_positions')
```



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------
::: aside
```{r education_aside}
CV %<>% print_text_block('education_aside')
```
:::

```{r education}
CV %<>% print_section('education')
```


<!--
Teaching Experience {data-icon=chalkboard-teacher}

--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('teaching_positions')
```
-->
<br>

Selected Publications 
--------------------------------------------------------------------------------

::: aside
I advocate reproducible and transparent computational research and have published books of narratives and reproducible code for our manuscripts on GitHub (examples [**1**](https://fredhutch.github.io/canFam3.DuxFamily/) and [**2**](https://fredhutch.github.io/Wellstone_BiLateral_Biopsy/))

<br>
<br>
Made with the R packages [**datadrivencv**](https://github.com/nstrayer/datadrivencv) and [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r Sys.Date()`.
:::

```{r}
CV %<>% print_section('academic_articles')
```

